Verifying Demonstrations

### 2020-03-13 paper/intro.tex
adds reference to related work section in outline
Adds brief intro

@@

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the DFKO 
model~\cite{DB-DFKO,FormalTerroristFraud,TREAD}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is reasonable by the results of \textcite{UWBPR}.

>>>>

Although there are numerous contributions in the field of \ac{DB} 
authentication protocols, the majority of them are shared-key protocols.
This means that the prover and the verifier must share a secret.
This might work for key-less entry protocols for cars, where the car and keyfob 
can share a key.
But it does not work for ubiquitous \ac{DB} authentication.

Our work present contributions in the area of \ac{DB} public-key protocols, 
particularly \ac{DB} \ac{ZKPK}.
This allows anyone to act as a verifier, unlike in the shared-key scenario 
where the verifier must be trusted.
The \ac{ZK} property also enables privacy properties such as anonymity.

@@

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is reasonable by the results of \textcite{UWBPR}.
